### 2012-09-04 sections/introduction.tex
Add flowy/NFQL history

In this paper, we introduce \ac{NFQL}, an efficient C implementation of the
flow query language. It is the next iteration of the first prototype
implementation, Flowy \cite{kkanev:2010}, which was written in Python.
\ac{NFQL}, however, is not just a reimplementation in a new language, but the
inner workings have been reimagined to allow the execution engine to scale to
real-world sized traces. This has been possible by replacing the performance
critical stages of the pipeline with crispier algorithms that lower the
execution times, making \ac{NFQL} comparable to contemporary flow analysis
tools.

>>>>

Flowy \cite{kkanev:2010} was a first feature complete Python prototype of that
flow query language. Due to performance problems, it was superseeded by a
complete rewrite in C, called Flowy 2.0 \cite{jschauer:thesis:2011}. In this
paper, we introduce \ac{NFQL} which extends on Flowy 2.0, making it more
feature complete and optimizing its execution engine with crispier algorithms.
We show that this iteration of our work is able to scale to real-world sized
traces and has comparable execution times to contemporary flow analysis tools.
